### 2014-02-20 paper/retrofit.tex
color vars

\begin{figure}
\begin{code}
tv   ::= \x.te | true | false | ta
te   ::= tv | x | te te | if te then te else te | ref te | !te | te := te | diverge
tE   ::= tE te | tv tE | if tE then te else te
       | ref tE | !tE | tE := te | tv := tE

te1 ; te2           @= (\x.te2) te1  where  x notmember FV(te2)
let x = te1 in te2  @= (\x.te2) te1
\end{code}

@@

\begin{figure}
\begin{code}
lop  ::=  canFlowTo | lub | glb
iv   ::=  id | il | true | false | unit
ie   ::=  iv | x | y | ie lop ie | getLabel | setLabel ie
       |  fork ie | send ie ie ie | x, y <= recv. ie ie |  IT te
iE   ::=  iE lop ie | iv lop iE | setLabel iE | fork iE 
       |  send iE ie ie | send iv iE ie | send iv iv iE
       |  x, y <= recv. ie ie |  IT tE
Q    ::=  nil | (il, id, ie) :: Q

tE   ::=  cdots | TI iE

x, y <= brecv . ie @= IT (let te' = TI (x, y <= recv. ie  (IT te')) in te')
\end{code}

\begin{mathpar}
\inferrule[I-getLabel]
{ }
{|
iconf iS (lconf id il tS (iniE (getLabel)), ldots)
-->
iconf iS (lconf id il tS (iniE il), ldots)
|}
\and
\inferrule[I-setLabel]
{ |il canFlowTo il'| }
{|
iconf iS (lconf id il tS (iniE (setLabel il')), ldots)
-->
iconf iS (lconf id il' tS (iniE unit), ldots)
|}
\and
\inferrule[I-fork]
{ 
|iS' = iS [ id' mapsto nil ]|
}
{|
iconf iS (lconf id il tS (iniE (fork (IT te))), ldots)
-->
iconf iS' (lconf id il tS (iniE id'), ldots, lconf id' il tS te)
|}
{|fresh (id')|}
\and
\inferrule[I-send]
{
|il canFlowTo il'|\\
|iS(id') = Q|\\
|iS' = iS [ id' mapsto (il', id,  ie) :: Q ]|
}
{|
iconf iS (lconf id il tS (iniE (send id' il' ie))), ldots)
-->
iconf iS' (lconf id il tS (iniE unit), ldots)
|}
\and
\inferrule[I-recv]
{
| filter il (iS(id)) = (il', id', ie') :: Q'|\\
| iS' = iS[id mapsto Q']|
}
{|
iconf iS (lconf id il tS (iniE (x, y <= recv. ie1 ie2))), ldots)
-->
iconf iS' (lconf id il tS (iniE ({ie'/x,id'/y} ie1)), ldots)
|}
\and
\inferrule[I-noRecv]
{
| filter il (iS(id)) = nil|\\
| iS' = iS[id mapsto nil]|
}
{|
iconf iS (lconf id il tS (iniE (x, y <= recv. ie1 ie2))), ldots)
-->
iconf iS' (lconf id il tS (iniE ie2), ldots)
|}
\and
\inferrule[I-border]
{ }
{| iniE (IT (TI (ie))) --> iniE ie |}
\and
\inferrule[T-border]
{ }
{| intE (TI (IT (te))) --> intE te |}
\end{mathpar}

@@

\cut{
(Selected rules from evaluation semantics. It's typed in the usual way.)

(Maybe this section needs to get moved) Sketch how a traditional account
of IFC would go about extending these rules.  These things are:

\begin{enumerate}
    \item Extend values with labels. (Values are isolated in runtimes,
        so runtime is labeled not values)
    \item Extend semantics to have a label on the program counter.
        (Ditto, runtime is values.)
    \item Extend semantics for assignment, as addresses need labels.
        (Labeled references are internalized in IFC language, and
        traditional references are isolated in runtimes.)
    \item Flow-sensitivity/insensitivity? (We choose flow-insensitive,
        flow sensitivity by reduction.)
\end{enumerate}

% No longer describing a "minimal non-Turing complete IFC calculus",
% instead, we jump straight to the combination.

We'd like to construct a coarse-grained IFC system on top of our language.
Intuitively, programs written in the target language are running on top of
an IFC ``operating system''.  The way we will perform our embedding is
by allowing programs to perform ``syscalls'' into the IFC runtime, and
vice-versa.  The IFC runtime is responsible for performing label checks
and ensuring TSNI is not violated.

We achieve this using a Matthews-Findler style embedding~\nocite{} to combine
the IFC language from the previous section with our example language.  Key points:

\Red{EZY reviewer hat: why is this type mediation necessary? It seems a bit
over-the-top.}

\begin{itemize}
    \item Expression and evaluation contexts are considered separately,
        so that some of our operational rules are easier to write
    \item IT/TI mediate cross-language type boundary (mention that this
        is where monitor failure/exceptions get handled)
\end{itemize}

First, we associate a label with every evaluation context.  Suppose you had
a function \verb|readFile|, you need to raise your label to write this
kind of program.

Motivate why we have labeled values. How to I avoid label creep problem? We
have fork. \Red{EZY shouldn't be in the ``background'' section.}

Background talks about IFC calculus in general; here we talk about
embedding and give the precise semantics for the IFC embedding.

\Red{Give a fake rule with how you raise your label when you read from a file.
We give you labeled values explicitly.}

\Red{EZY Why wouldn't a reviewer say, this sendMessage/receiveMessage thing
is pretty weird, why'd you do the API that way?}

\begin{verbatim}
% colored differently
e ::= fork e
    # let's do channels?
    | sendMessage e e  # asynchronous
    | receiveMessage e # registers the callback
    | label e e
    | unlabel e
    | IT e

v ::= tid
    | l
    | Labeled l v
\end{verbatim}

\Red{Prove type safety for combined language?}

\Red{Problem: synchronization primitives which are blocking. OK, talk
about this at the end. You can do whatever you want.}
% NB: the nice thing about sendMessage is we can just drop messages
% when the labels don't work out
%
% Intuitively, it would seem to me that any concurrency primitive
% would be fine, as long as you proved it safe, we don't really care.

(Full operational semantics. Provide type rules.)

\Red{What to do when you get stuck when you are about to invalidate IFC}

Which rules do we want to talk about?

\begin{enumerate}
\item fork: most complicated; shows side-condition (what do we do with stores on fork?)
\item label:  shows side-condition (what can we label? same as fork, but empty/all stores)
\item unlabel: shows raising of label
\item sendMessage: will give type for (maybe encapsulate queue in env)
\end{enumerate}

\subsection{The methodology (XXX fix title)}
\label{sec:methodology}

We now formally state our information-flow control transformation.  For
simplicity's sake, we consider only single-threaded source languages,
whose primary notion of execution is evaluation of an expression into a
value.  (Later, we consider how to accomodate systems which have
semantics for concurrent execution.)

\subsection{A tiny information-flow control calculus}

\begin{figure}[h]
\begin{align*}
\textrm{Thread \#:}   && \Ii          &   \\
\textrm{Label:}       && \Il          & \ \ \text{(we additionally use \Ic{} for clearances)}  \\
\textrm{Label op:}    && \ifc{\oplus} & ::=  \ifc{\lub}
                                        \ |\ \ifc{\glb}
                                        \ |\ \ifc{\flows}\\
\textrm{Value:}       && \Iv          & ::=  \Itrue 
                                        \ |\ \Ifalse
                                        \ |\ \Iunit
                                        \ |\ \Il
                                        \ |\ \Ierr
                                        \ |\ \Ii\\
%                                        \ |\ \IT{\Tv}{\Tstore}{\Tenv}\\
\textrm{Expression:}  && \Ie          & ::=  \Iv
                                        \ |\ \Ilop{\Ie}{\Ie}
                                        \ |\ \IgetLabel
                                        \ |\ \IgetClr\\&&&
                                        \ |\ \Ifork{\Ie}{\Ie}
                                        \ |\ \IT{\Te}\\
\textrm{Context:}     && \IE          & ::=  \Ihole{\ }
                                        \ |\ \Ilop{\IE}{\Ie}
                                        \ |\ \Ilop{\Iv}{\IE}\\&&&
                                        \ |\ \Ifork{\IE}{\Ie}
                                        \ |\ \Ifork{\Iv}{\IE}
                                        \ |\ \IT{\TE}\\
\textrm{Store (of target language):} && \Istore\\
\textrm{Prim label op:} && \denot{\cdot}   & \in \Ie \rightharpoonup \Iv \\
\end{align*}
% reduction rules
\begin{mathpar}

\inferrule[I-target]{
  \Tconf{\Tstore}{\Tenv}{\inTE{\Te}}
  \Tarrow
  \Tconf{\tar{\Tstore'}}{\Tenv'}{\inTE{\tar{\Te'}}}
  \\
  \TIstore{\Tstore}{\Tenv} = \Istore
  \\
  \TIstore{\tar{\Tstore'}}{\tar{\Tenv'}} = \ifc{\Istore'}
}
{
  \Iconf{\Istore}{\Il}{\Ic}{\inTE{\Te}}\Itasksep\cdots
  \Iarrow
  \Iconf{\ifc{\Istore'}}{\Il}{\Ic}{\inTE{\tar{\Te'}}}\Itasksep\cdots
}

\and

\inferrule[I-boundary]{ }
{
  \Iconf{\Istore}{\Il}{\Ic}{\inTE{\TI{\IT{\Te}}}}
  \Iarrow
  \Iconf{\Istore}{\Il}{\Ic}{\inTE{\Te}}
}

\and

\inferrule[I-label]{ }
{
  \Iconf{\Istore}{\Il}{\Ic}{\inTE{\TI{\IgetLabel}}}\Itasksep\cdots
  \Iarrow
  \Iconf{\Istore}{\Il}{\Ic}{\inTE{\TI{\Il}}}\Itasksep\cdots
}

\and

\inferrule[I-clearance]{ }
{
  \Iconf{\Istore}{\Il}{\Ic}{\inTE{\TI{\IgetClr}}}\Itasksep\cdots
  \Iarrow
  \Iconf{\Istore}{\Il}{\Ic}{\inTE{\TI{\Ic}}}\Itasksep\cdots
}

% fork
\inferrule[I-fork]
{ 
  \denot{\Iflows{\Il}{\ifc{\Il'}}} = \Itrue\\
  \denot{\Iflows{\ifc{\Il'}}{\Ic}} = \Itrue\\
  \ifc{\Istore'} = \Tklone(\Istore)\\
}
{
  \Iconf{\Istore}{\Tenv}{\Il}{\Ic}{
    \inTE{\TI{
      (\Ifork{\Il'}{(\IT{\Te})})
    }}
  }
  \Itasksep\cdots
  %
  \Iarrow
  %
  \Iconf{\Istore}{\Il}{\Ic}{\inTE{\TI{\Ii}}}
  \Itasksep\cdots\Itasksep
  \Iconf{\ifc{\Istore'}}{\Il}{\Il}{\inTE{\Te}}
  \Itasksep\cdots
}{\operatorname{fresh}(\Ii)}

\end{mathpar}

\caption{IFC calculus}
\end{figure}

\begin{figure}[h]
\begin{align*}
\textrm{Address:}     && \Ta          & \\
\textrm{Variable:}    && \Tx          & \\
\textrm{Value:}       && \Tv          & ::= \Tclo{\Tlambda{\Tx}{\Te}}{\Tenv}\\
\textrm{Expression:}  && \Te          & ::=  \Tv
                                        \ |\ \Tlambda{\Tx}{\Te}
                                        \ |\ \Tx
                                        \ |\ \Te\ \Te
                                        \ |\ \Tset{\Te}{\Te}
                                        \ |\ \TI{\Ie}\\
\textrm{Context:}     && \TE          & ::=  \Thole{\ }
                                        \ |\ \TE\ \Te
                                        \ |\ \Tv\ \TE\\&&&
                                        \ |\ \Tset{\TE}{\Te}
                                        \ |\ \Tset{\Tx}{\TE}
                                        \ |\ \TI{\IE}\\
\textrm{Environment:} && \Tenv        & \in \Tx \rightharpoonup \Ta \\
\textrm{Store:}       && \Tstore      & \in \Ta \rightharpoonup \Tv \\
\textrm{Klone:}       && \Tklone   & \in \Tenv \times \Tstore \rightharpoonup \Tenv \times \Tstore \\
\end{align*}
% reduction rules
\begin{mathpar}

% lambda to closure
\inferrule[T-lam]{ }
{
\Tconf{\Tstore}{\Tenv}{\inTE{\Tlambda{\Tx}{\Te}}}
\Tarrow
\Tconf{\Tstore}{\Tenv}{\inE{\Tclo{\Tlambda{\Tx}{\Te}}{\Tenv}}}
}

\and

% lookup variable
\inferrule[T-var]{ }
{
\Tconf{\Tstore}{\Tenv}{\inTE{\Tx}}
\Tarrow
\Tconf{\Tstore}{\Tenv}{\inE{\Tstore(\Tenv(\Tx))}}
}

\and

% beta reduction
\inferrule[T-$\beta$]
{
\tar{\Tstore'}=\Tstore[\Ta \mapsto \Tv]\\
\tar{\Tenv''} =\tar{\Tenv'}[\Tx \mapsto \Ta]
}
{
\Tconf{\Tstore}{\Tenv}{\inTE{\Tclo{\Tlambda{\Tx}{\Te}}{\tar{\Tenv'}}\ \Tv}}
\Tarrow
\Tconf{\tar{\Tstore'}}{\tar{\Tenv''}}{\inE{\Te}}
}{\operatorname{fresh}(\Ta)}

\and

% set!
\inferrule[T-set]
{
\tar{\store'} = \Tstore[\Tenv(\Tx) \mapsto \Tv]
}
{
\Tconf{\Tstore}{\Tenv}{\inTE{\Tset{\Tx}{\Tv}}}
\Tarrow
\Tconf{\tar{\store'}}{\Tenv}{\inE{\Tv}}
}
% fork
%\inferrule[E-fork]
%{ 
%\Iflows{\Il}{\Il} \Ilabelarrow \Itrue\\
%\Iflows{\Il}{\Ic} \Ilabelarrow \Itrue\\
%\tar{\Tstore'} = \Tklone{\Tstore}(\Tstore)\\
%\tar{\Tenv'}   = \Tklone{\Tenv}(\Tenv)
%}
%{
%\Iconf{\Il}{\Ic}{\inIE{ \Ifork{\Il}{
%      (\downcall{(\upcall{^{\Tstore}_{\Tenv}\ \Ie})})
%}}}\|\cdots
%\to
%\Iconf{\Il}{\Ic}{\inE{\Ii}}\|\cdots\|
%\Iconf{\Il}{\Il}{\inE{
%}}\|\cdots
%}{fresh(\Ii)}

\end{mathpar}
\caption{Simple calculus}
\end{figure}

Our first task is to define a information-flow control mini-language
which will be combined with the source language. (Reference)  This
language is not Turing-complete; this is intentional, as (1) the ability
to call across the language boundary means that any control flow can be
implemented in the source language, and (2) it simplifies the
non-interference proof.  The language has a very simple set of typing
rules.  The operational semantics for this language are worth remarking
on (write a bit about how this IFC system works).  We can now state and
prove a simple non-interference theorem about this language:

\begin{theorem}
(Statement of noninterference)
\end{theorem}
\begin{proof}
XXX TODO should be simple
\end{proof}

\subsection{Combination (XXX)}

}

>>>>

\begin{figure}
\begin{code}
tv   ::= \tx.te | true | false | ta
te   ::= tv | tx | te te | if te then te else te | ref te | !te | te := te | diverge
tE   ::= tE te | tv tE | if tE then te else te
       | ref tE | !tE | tE := te | tv := tE

te1 ; te2            @= (\tx.te2) te1  where  tx notmember FV(te2)
let tx = te1 in te2  @= (\tx.te2) te1
\end{code}

@@

\begin{figure}
\begin{code}
lop  ::=  canFlowTo | lub | glb
iv   ::=  id | il | true | false | unit
ie   ::=  iv | ix | ie lop ie | getLabel | setLabel ie
       |  fork ie | send ie ie ie | ix1, ix2 <= recv. ie ie |  IT te
iE   ::=  iE lop ie | iv lop iE | setLabel iE | fork iE 
       |  send iE ie ie | send iv iE ie | send iv iv iE
       |  ix1, ix2 <= recv. ie ie |  IT tE
Q    ::=  nil | (il, id, ie) :: Q

te   ::=  cdots | TI ie
tE   ::=  cdots | TI iE

ix1, ix2 <= brecv . ie @= IT (let tx = TI (ix1, ix2 <= recv. ie  (IT tx)) in tx)
\end{code}

\begin{mathpar}
\inferrule[I-getLabel]
{ }
{|
iconf iS (lconf id il tS (iniE (getLabel)), ldots)
-->
iconf iS (lconf id il tS (iniE il), ldots)
|}
\and
\inferrule[I-setLabel]
{ |il canFlowTo il'| }
{|
iconf iS (lconf id il tS (iniE (setLabel il')), ldots)
-->
iconf iS (lconf id il' tS (iniE unit), ldots)
|}
\and
\inferrule[I-fork]
{ 
|iS' = iS [ id' mapsto nil ]|\\
|tS' = q(tS)|
}
{|
iconf iS (lconf id il tS (iniE (fork ie)), ldots)
-->
iconf iS' (lconf id il tS (iniE id'), ldots, lconf id' il tS' (TI ie))
|}
{|fresh (id')|}
\and
\inferrule[I-send]
{
|il canFlowTo il'|\\
|iS(id') = Q|\\
|iS' = iS [ id' mapsto (il', id,  ie) :: Q ]|
}
{|
iconf iS (lconf id il tS (iniE (send id' il' ie))), ldots)
-->
iconf iS' (lconf id il tS (iniE unit), ldots)
|}
\and
\inferrule[I-recv]
{
| filter il (iS(id)) = (il', id', ie') :: Q'|\\
| iS' = iS[id mapsto Q']|
}
{|
iconf iS (lconf id il tS (iniE (ix1, ix2 <= recv. ie1 ie2))), ldots)
-->
iconf iS' (lconf id il tS (iniE ({ie'/ix1,id'/ix2} ie1)), ldots)
|}
\and
\inferrule[I-noRecv]
{
| filter il (iS(id)) = nil|\\
| iS' = iS[id mapsto nil]|
}
{|
iconf iS (lconf id il tS (iniE (ix1, ix2 <= recv. ie1 ie2))), ldots)
-->
iconf iS' (lconf id il tS (iniE ie2), ldots)
|}
\and
\inferrule[I-bool]
{ |b member {true, false}|  } {| iniE (IT b) --> iniE b |}
\and
\inferrule[I-border]
{ } {| iniE (IT (TI (ie))) --> iniE ie |}
\and
\inferrule[T-bool]
{ |b member {true, false}| } {| intE (TI b) --> intE b |}
\and
\inferrule[T-border]
{ } {| intE (TI (IT (te))) --> intE te |}
\end{mathpar}

@@

The filter function |filter il Q| removes message whose labels do not
flow to |il|. Specifically, if |Q| is the empty list |nil|, the
function is simply the identity function, i.e.,
|filter il nil = nil|; otherwise:
\[
|filter il ((il', id, ie) :: Q )| = \left\{
\begin{array}{l l}
|(il', id, ie) :: filter il Q| & \quad \text{if |il' canFlowTo il|}\\
|filter il Q| & \quad \text{otherwise}
\end{array} \right.
\]

%% \cut{
%% (Selected rules from evaluation semantics. It's typed in the usual way.)
%% 
%% (Maybe this section needs to get moved) Sketch how a traditional account
%% of IFC would go about extending these rules.  These things are:
%% 
%% \begin{enumerate}
%%     \item Extend values with labels. (Values are isolated in runtimes,
%%         so runtime is labeled not values)
%%     \item Extend semantics to have a label on the program counter.
%%         (Ditto, runtime is values.)
%%     \item Extend semantics for assignment, as addresses need labels.
%%         (Labeled references are internalized in IFC language, and
%%         traditional references are isolated in runtimes.)
%%     \item Flow-sensitivity/insensitivity? (We choose flow-insensitive,
%%         flow sensitivity by reduction.)
%% \end{enumerate}
%% 
%% % No longer describing a "minimal non-Turing complete IFC calculus",
%% % instead, we jump straight to the combination.
%% 
%% We'd like to construct a coarse-grained IFC system on top of our language.
%% Intuitively, programs written in the target language are running on top of
%% an IFC ``operating system''.  The way we will perform our embedding is
%% by allowing programs to perform ``syscalls'' into the IFC runtime, and
%% vice-versa.  The IFC runtime is responsible for performing label checks
%% and ensuring TSNI is not violated.
%% 
%% We achieve this using a Matthews-Findler style embedding~\nocite{} to combine
%% the IFC language from the previous section with our example language.  Key points:
%% 
%% \Red{EZY reviewer hat: why is this type mediation necessary? It seems a bit
%% over-the-top.}
%% 
%% \begin{itemize}
%%     \item Expression and evaluation contexts are considered separately,
%%         so that some of our operational rules are easier to write
%%     \item IT/TI mediate cross-language type boundary (mention that this
%%         is where monitor failure/exceptions get handled)
%% \end{itemize}
%% 
%% First, we associate a label with every evaluation context.  Suppose you had
%% a function \verb|readFile|, you need to raise your label to write this
%% kind of program.
%% 
%% Motivate why we have labeled values. How to I avoid label creep problem? We
%% have fork. \Red{EZY shouldn't be in the ``background'' section.}
%% 
%% Background talks about IFC calculus in general; here we talk about
%% embedding and give the precise semantics for the IFC embedding.
%% 
%% \Red{Give a fake rule with how you raise your label when you read from a file.
%% We give you labeled values explicitly.}
%% 
%% \Red{EZY Why wouldn't a reviewer say, this sendMessage/receiveMessage thing
%% is pretty weird, why'd you do the API that way?}
%% 
%% \begin{verbatim}
%% % colored differently
%% e ::= fork e
%%     # let's do channels?
%%     | sendMessage e e  # asynchronous
%%     | receiveMessage e # registers the callback
%%     | label e e
%%     | unlabel e
%%     | IT e
%% 
%% v ::= tid
%%     | l
%%     | Labeled l v
%% \end{verbatim}
%% 
%% \Red{Prove type safety for combined language?}
%% 
%% \Red{Problem: synchronization primitives which are blocking. OK, talk
%% about this at the end. You can do whatever you want.}
%% % NB: the nice thing about sendMessage is we can just drop messages
%% % when the labels don't work out
%% %
%% % Intuitively, it would seem to me that any concurrency primitive
%% % would be fine, as long as you proved it safe, we don't really care.
%% 
%% (Full operational semantics. Provide type rules.)
%% 
%% \Red{What to do when you get stuck when you are about to invalidate IFC}
%% 
%% Which rules do we want to talk about?
%% 
%% \begin{enumerate}
%% \item fork: most complicated; shows side-condition (what do we do with stores on fork?)
%% \item label:  shows side-condition (what can we label? same as fork, but empty/all stores)
%% \item unlabel: shows raising of label
%% \item sendMessage: will give type for (maybe encapsulate queue in env)
%% \end{enumerate}
%% 
%% \subsection{The methodology (XXX fix title)}
%% \label{sec:methodology}
%% 
%% We now formally state our information-flow control transformation.  For
%% simplicity's sake, we consider only single-threaded source languages,
%% whose primary notion of execution is evaluation of an expression into a
%% value.  (Later, we consider how to accomodate systems which have
%% semantics for concurrent execution.)
%% 
%% \subsection{A tiny information-flow control calculus}
%% 
%% \begin{figure}[h]
%% \begin{align*}
%% \textrm{Thread \#:}   && \Ii          &   \\
%% \textrm{Label:}       && \Il          & \ \ \text{(we additionally use \Ic{} for clearances)}  \\
%% \textrm{Label op:}    && \ifc{\oplus} & ::=  \ifc{\lub}
%%                                         \ |\ \ifc{\glb}
%%                                         \ |\ \ifc{\flows}\\
%% \textrm{Value:}       && \Iv          & ::=  \Itrue 
%%                                         \ |\ \Ifalse
%%                                         \ |\ \Iunit
%%                                         \ |\ \Il
%%                                         \ |\ \Ierr
%%                                         \ |\ \Ii\\
%% %                                        \ |\ \IT{\Tv}{\Tstore}{\Tenv}\\
%% \textrm{Expression:}  && \Ie          & ::=  \Iv
%%                                         \ |\ \Ilop{\Ie}{\Ie}
%%                                         \ |\ \IgetLabel
%%                                         \ |\ \IgetClr\\&&&
%%                                         \ |\ \Ifork{\Ie}{\Ie}
%%                                         \ |\ \IT{\Te}\\
%% \textrm{Context:}     && \IE          & ::=  \Ihole{\ }
%%                                         \ |\ \Ilop{\IE}{\Ie}
%%                                         \ |\ \Ilop{\Iv}{\IE}\\&&&
%%                                         \ |\ \Ifork{\IE}{\Ie}
%%                                         \ |\ \Ifork{\Iv}{\IE}
%%                                         \ |\ \IT{\TE}\\
%% \textrm{Store (of target language):} && \Istore\\
%% \textrm{Prim label op:} && \denot{\cdot}   & \in \Ie \rightharpoonup \Iv \\
%% \end{align*}
%% % reduction rules
%% \begin{mathpar}
%% 
%% \inferrule[I-target]{
%%   \Tconf{\Tstore}{\Tenv}{\inTE{\Te}}
%%   \Tarrow
%%   \Tconf{\tar{\Tstore'}}{\Tenv'}{\inTE{\tar{\Te'}}}
%%   \\
%%   \TIstore{\Tstore}{\Tenv} = \Istore
%%   \\
%%   \TIstore{\tar{\Tstore'}}{\tar{\Tenv'}} = \ifc{\Istore'}
%% }
%% {
%%   \Iconf{\Istore}{\Il}{\Ic}{\inTE{\Te}}\Itasksep\cdots
%%   \Iarrow
%%   \Iconf{\ifc{\Istore'}}{\Il}{\Ic}{\inTE{\tar{\Te'}}}\Itasksep\cdots
%% }
%% 
%% \and
%% 
%% \inferrule[I-boundary]{ }
%% {
%%   \Iconf{\Istore}{\Il}{\Ic}{\inTE{\TI{\IT{\Te}}}}
%%   \Iarrow
%%   \Iconf{\Istore}{\Il}{\Ic}{\inTE{\Te}}
%% }
%% 
%% \and
%% 
%% \inferrule[I-label]{ }
%% {
%%   \Iconf{\Istore}{\Il}{\Ic}{\inTE{\TI{\IgetLabel}}}\Itasksep\cdots
%%   \Iarrow
%%   \Iconf{\Istore}{\Il}{\Ic}{\inTE{\TI{\Il}}}\Itasksep\cdots
%% }
%% 
%% \and
%% 
%% \inferrule[I-clearance]{ }
%% {
%%   \Iconf{\Istore}{\Il}{\Ic}{\inTE{\TI{\IgetClr}}}\Itasksep\cdots
%%   \Iarrow
%%   \Iconf{\Istore}{\Il}{\Ic}{\inTE{\TI{\Ic}}}\Itasksep\cdots
%% }
%% 
%% % fork
%% \inferrule[I-fork]
%% { 
%%   \denot{\Iflows{\Il}{\ifc{\Il'}}} = \Itrue\\
%%   \denot{\Iflows{\ifc{\Il'}}{\Ic}} = \Itrue\\
%%   \ifc{\Istore'} = \Tklone(\Istore)\\
%% }
%% {
%%   \Iconf{\Istore}{\Tenv}{\Il}{\Ic}{
%%     \inTE{\TI{
%%       (\Ifork{\Il'}{(\IT{\Te})})
%%     }}
%%   }
%%   \Itasksep\cdots
%%   %
%%   \Iarrow
%%   %
%%   \Iconf{\Istore}{\Il}{\Ic}{\inTE{\TI{\Ii}}}
%%   \Itasksep\cdots\Itasksep
%%   \Iconf{\ifc{\Istore'}}{\Il}{\Il}{\inTE{\Te}}
%%   \Itasksep\cdots
%% }{\operatorname{fresh}(\Ii)}
%% 
%% 
%% \end{mathpar}
%% 
%% \caption{IFC calculus}
%% \end{figure}
%% 
%% \begin{figure}[h]
%% \begin{align*}
%% \textrm{Address:}     && \Ta          & \\
%% \textrm{Variable:}    && \Tx          & \\
%% \textrm{Value:}       && \Tv          & ::= \Tclo{\Tlambda{\Tx}{\Te}}{\Tenv}\\
%% \textrm{Expression:}  && \Te          & ::=  \Tv
%%                                         \ |\ \Tlambda{\Tx}{\Te}
%%                                         \ |\ \Tx
%%                                         \ |\ \Te\ \Te
%%                                         \ |\ \Tset{\Te}{\Te}
%%                                         \ |\ \TI{\Ie}\\
%% \textrm{Context:}     && \TE          & ::=  \Thole{\ }
%%                                         \ |\ \TE\ \Te
%%                                         \ |\ \Tv\ \TE\\&&&
%%                                         \ |\ \Tset{\TE}{\Te}
%%                                         \ |\ \Tset{\Tx}{\TE}
%%                                         \ |\ \TI{\IE}\\
%% \textrm{Environment:} && \Tenv        & \in \Tx \rightharpoonup \Ta \\
%% \textrm{Store:}       && \Tstore      & \in \Ta \rightharpoonup \Tv \\
%% \textrm{Klone:}       && \Tklone   & \in \Tenv \times \Tstore \rightharpoonup \Tenv \times \Tstore \\
%% \end{align*}
%% % reduction rules
%% \begin{mathpar}
%% 
%% % lambda to closure
%% \inferrule[T-lam]{ }
%% {
%% \Tconf{\Tstore}{\Tenv}{\inTE{\Tlambda{\Tx}{\Te}}}
%% \Tarrow
%% \Tconf{\Tstore}{\Tenv}{\inE{\Tclo{\Tlambda{\Tx}{\Te}}{\Tenv}}}
%% }
%% 
%% \and
%% 
%% % lookup variable
%% \inferrule[T-var]{ }
%% {
%% \Tconf{\Tstore}{\Tenv}{\inTE{\Tx}}
%% \Tarrow
%% \Tconf{\Tstore}{\Tenv}{\inE{\Tstore(\Tenv(\Tx))}}
%% }
%% 
%% \and
%% 
%% % beta reduction
%% \inferrule[T-$\beta$]
%% {
%% \tar{\Tstore'}=\Tstore[\Ta \mapsto \Tv]\\
%% \tar{\Tenv''} =\tar{\Tenv'}[\Tx \mapsto \Ta]
%% }
%% {
%% \Tconf{\Tstore}{\Tenv}{\inTE{\Tclo{\Tlambda{\Tx}{\Te}}{\tar{\Tenv'}}\ \Tv}}
%% \Tarrow
%% \Tconf{\tar{\Tstore'}}{\tar{\Tenv''}}{\inE{\Te}}
%% }{\operatorname{fresh}(\Ta)}
%% 
%% \and
%% 
%% % set!
%% \inferrule[T-set]
%% {
%% \tar{\store'} = \Tstore[\Tenv(\Tx) \mapsto \Tv]
%% }
%% {
%% \Tconf{\Tstore}{\Tenv}{\inTE{\Tset{\Tx}{\Tv}}}
%% \Tarrow
%% \Tconf{\tar{\store'}}{\Tenv}{\inE{\Tv}}
%% }
%% % fork
%% %\inferrule[E-fork]
%% %{ 
%% %\Iflows{\Il}{\Il} \Ilabelarrow \Itrue\\
%% %\Iflows{\Il}{\Ic} \Ilabelarrow \Itrue\\
%% %\tar{\Tstore'} = \Tklone{\Tstore}(\Tstore)\\
%% %\tar{\Tenv'}   = \Tklone{\Tenv}(\Tenv)
%% %}
%% %{
%% %\Iconf{\Il}{\Ic}{\inIE{ \Ifork{\Il}{
%% %      (\downcall{(\upcall{^{\Tstore}_{\Tenv}\ \Ie})})
%% %}}}\|\cdots
%% %\to
%% %\Iconf{\Il}{\Ic}{\inE{\Ii}}\|\cdots\|
%% %\Iconf{\Il}{\Il}{\inE{
%% %}}\|\cdots
%% %}{fresh(\Ii)}
%% 
%% 
%% \end{mathpar}
%% \caption{Simple calculus}
%% \end{figure}
%% 
%% Our first task is to define a information-flow control mini-language
%% which will be combined with the source language. (Reference)  This
%% language is not Turing-complete; this is intentional, as (1) the ability
%% to call across the language boundary means that any control flow can be
%% implemented in the source language, and (2) it simplifies the
%% non-interference proof.  The language has a very simple set of typing
%% rules.  The operational semantics for this language are worth remarking
%% on (write a bit about how this IFC system works).  We can now state and
%% prove a simple non-interference theorem about this language:
%% 
%% \begin{theorem}
%% (Statement of noninterference)
%% \end{theorem}
%% \begin{proof}
%% XXX TODO should be simple
%% \end{proof}
%% 
%% \subsection{Combination (XXX)}
%% 
%% 
%% }
